---
title: "A simple report"
author: "Your name"
date: "`r format(Sys.time(), '%a %d %b %Y (%H:%M:%S)')`"
output:
  html_document: default
  bookdown::word_document2: default
---


```{r setup, include=FALSE}
# How to set up a document:
# in the first chunk we load package and data for the document

# load package that will be used later in the document
library('tidyverse')

# load data which are store in the Data folder a the root of the project directory
load('../../Data/df_data_survey.RData')
```


# Getting Started
The dataset used in this report is structured as:
```{r head data}
head(df_data, n = 5)
```

There are `r dim(df_data)[1]` rows in our dataset. Our data frame is based on the *Hecate Strait Synoptic Trawl Survey* and **simulated data**. 

# Plot data
## Scatter plot: Depth and Biomass
```{r sp_base, eval = TRUE}
sp <- ggplot(data=df_data, aes(x=Avg_net_depth, y=Biomass)) +
  geom_point(size=1)
print(sp)
```

To print the R code used to plot the data without running it use eval = FALSE in the chunk option:

```{r sp_base_no_eval, eval = FALSE}
sp <- ggplot(data=df_data, aes(x=Avg_net_depth, y=Biomass)) +
  geom_point(size=1)
print(sp)
```

and if we don't want to show the R code

```{r sp_base_no_code, eval = TRUE, echo = FALSE}
sp <- ggplot(data=df_data, aes(x=Avg_net_depth, y=Biomass)) +
  geom_point(size=1)
print(sp)
```

## Scatter plot with color: Depth and Biomass
```{r sp_color, eval=TRUE,  tidy=FALSE, opts.label='fig.medium'}
sp_color <- ggplot(df_data, aes(x=Avg_net_depth, y=Biomass,
                                color=AREA)) +
  geom_point(size=1)
print(sp_color)
```

# Math equation
We can use the LaTeX syntax to write math equations:

$$ Y \sim LogNormal(\mu, \sigma) $$

or for multiple equations :

\begin{align}
Y & \sim LogNormal(\mu, \sigma) \\ 
\mu &  = \alpha + \beta * \text{Depth} + \gamma * \text{Temperature} \\
\sigma &  \sim Uniform(0,10)
\end{align}

more detail can be found here :
<https://fr.wikibooks.org/wiki/LaTeX/%C3%89crire_des_math%C3%A9matiques>
or 
<https://rpi.edu/dept/arc/training/latex/LaTeX_symbols.pdf>



